\section{Build instructions}

The complete hardware design files are provided in the project repository under 
the \texttt{Hardware} directory. The board can be reproduced using the editable 
DipTrace design file, the exported Gerber archive, the bill of materials, and 
the pick-and-place file described in the Design files summary and Bill of 
materials summary.

\subsection{PCB fabrication and assembly}

The PCB was designed to be fabricated and assembled through a low-cost 
PCB manufacturing service such as JLCPCB. To reproduce the board, upload 
\texttt{Hardware/SimpleSBC_gerber.zip} to the PCB manufacturer and use the 
fabrication settings specified by the manufacturer for the submitted Gerber 
files. The component placement and sourcing information are provided in 
\texttt{Hardware/sbcPNP.csv} and \texttt{Hardware/sbcBOM.csv}. 
The reference designators in these files correspond directly to the 
designators in \texttt{Hardware/SimpleSBC.dip}.

Before ordering assembled boards, the bill of materials should be checked 
against current part availability. If any component is unavailable, the 
replacement part should be verified for footprint compatibility, electrical 
compatibility, and assembly compatibility. Particular care should be taken 
when substituting the Allwinner F1C200s processor, RP2040 microcontroller, 
SPI flash memories, USB-C controllers, voltage regulators, MOSFETs, and 
crystal oscillators, since these parts may affect boot, power sequencing, 
USB operation, or Linux compatibility.

\subsection{Design review before manufacture}

Prior to fabrication, open \texttt{Hardware/SimpleSBC.dip} in DipTrace and 
inspect the schematic and PCB layout. Confirm that the power rails, USB-C 
connectors, microSD interface, SPI flash, display interface, UART bridge, 
and user-accessible connectors match the intended revision of the hardware. 
The exported manufacturing files should be regenerated if any schematic or 
layout changes are made.

The design uses the Allwinner F1C200s as the primary Linux-capable processor. 
This device was selected because it provides a low-cost embedded Linux 
platform suitable for simple research instruments while avoiding the cost 
and size of a Raspberry Pi-class single-board computer. An RP2040 is 
included as a USB-to-UART bridge to simplify programming, debugging, and 
board bring-up. This choice reduces the need for external serial adapters 
during development and makes the board easier to reproduce in teaching or 
laboratory settings.

\subsection{Board bring-up}

After receiving the assembled PCB, visually inspect the board under 
magnification before applying power. Check for obvious solder bridges, 
missing components, incorrectly oriented components, or mechanical damage. 
Special attention should be given to fine-pitch ICs, USB-C connectors, the 
microSD socket, crystal oscillators, and power-management components.

Before inserting a microSD card or connecting the board to a host computer, 
check the resistance between each major power rail and ground. A near-short 
may indicate an assembly fault and should be investigated before power is 
applied. If a current-limited bench supply is available, power the board 
initially with a conservative current limit and monitor the input current.

Once the board passes visual and electrical inspection, connect the board 
over USB and verify that the RP2040 USB-to-UART bridge enumerates 
correctly on the host computer. The firmware for this bridge is 
provided in \texttt{Software/pico-uart-bridge}. If the bridge firmware 
must be rebuilt, use the files in that directory together with the 
Raspberry Pi Pico SDK as described in the included README file.

\subsection{Linux image preparation}

The embedded Linux image is built using the Buildroot external tree 
located in \texttt{Software/simple_sbc}. The primary board configuration 
is provided by \texttt{Software/simple_sbc/configs/f1c200s_simple_sbc_defconfig}. 
The board-specific device tree files are located in 
\texttt{Software/simple_sbc/board/simple_sbc/allwinner}. These files define the 
hardware interfaces used by the Linux kernel, including the processor configuration 
and board-level peripherals.

To build the image, configure Buildroot using the provided defconfig, 
then compile the image using the standard Buildroot workflow. 
The resulting image can be written to a microSD card. After writing the image, 
insert the microSD card into the board and apply power. Boot messages should 
be visible through the UART bridge.

\subsection{Software and display configuration}

The Buildroot tree includes board-specific files for image generation, 
boot configuration, root filesystem overlays, and Linux kernel patches. 
The patch located at \texttt{Software/simple_sbc/board/simple_sbc/patches/linux/6.14.1/0001-st7789v-support-dc-gpio-8bit-spi.patch} 
provides support for the ST7789V display interface used by the board. 
The root filesystem overlay includes startup scripts and demonstration files 
used to validate the hardware after boot.

After the board boots, confirm that the serial console is available, the microSD 
root filesystem is mounted, and the expected display or peripheral interfaces are 
detected. The included example files in the overlay directory may be used for simple 
functional testing.

\subsection{Enclosure fabrication}

The enclosure files are provided as \texttt{Hardware/Enclosure/SimpleSBC_EnclosureTop.stl} 
and \texttt{Hardware/Enclosure/SimpleSBC_EnclosureBottom.stl}. 
These parts may be fabricated using a standard 3D printer or an external printing 
service. After printing, place the assembled PCB in the bottom enclosure piece and 
verify that all connectors, buttons, and openings align before attaching the top piece.

If the design is modified, the enclosure should be checked against the updated board 
outline and connector locations. Minor dimensional adjustments may be required depending 
on the 3D printing process and material used.

\subsection{Safety considerations}

The board is intended for low-voltage embedded electronics development. 
However, the assembled PCB should still be inspected carefully before power is applied. 
Do not power the board if there are visible solder bridges, damaged components, 
or signs of overheating. During initial bring-up, use a current-limited supply where possible.

The board should not be connected directly to mains voltage. 
Any external power supply used with the board should be current-limited and appropriately rated. 
Components such as voltage regulators, MOSFETs, 
and USB-C power circuitry may become hot if incorrectly assembled, overloaded, or shorted. 
Disconnect power immediately if excessive current draw, heat, smoke, 
or unexpected behaviour is observed.
