\begin{tabu} to \linewidth {|X|X|X[1.5,1]|X[1.5,1]|}
\hline
\textbf{Design filename} & \textbf{File type} & \textbf{Open source license} & \textbf{Location of the file} \\hline

SimpleSBC.dip & DipTrace schematic and PCB design files & Apache-2.0 & Repository associated with this article \\hline

SimpleSBC_gerber.zip & Manufacturing files (Gerber, drill, fabrication outputs) & Apache-2.0 & Repository associated with this article \\hline

sbcBOM.csv & Bill of materials & Apache-2.0 & Repository associated with this article \\hline

sbcPNP.csv & Pick-and-place assembly file & Apache-2.0 & Repository associated with this article \\hline

SimpleSBC_EnclosureTop.stl, SimpleSBC_EnclosureBottom.stl & Mechanical enclosure CAD files & Apache-2.0 & Repository associated with this article \\hline

f1c200s_simple_sbc.dts, f1c200s_simple_sbc.dtsi & Linux device tree source files & Apache-2.0 & Repository associated with this article \\hline

f1c200s_simple_sbc_defconfig & Buildroot configuration files & Apache-2.0 & Repository associated with this article \\hline

pico-uart-bridge & RP2040 USB-to-UART firmware source code & Apache-2.0 & Repository associated with this article \\hline

0001-st7789v-support-dc-gpio-8bit-spi.patch & Linux kernel patch enabling LCD support & Apache-2.0 & Repository associated with this article \\hline

\end{tabu}

\vskip 0.3cm

\textbf{SimpleSBC.dip} \
DipTrace project containing the complete schematic and PCB layout of the single-board computer. This file may be modified to adapt the design to alternative research applications or form factors.

\textbf{SimpleSBC_gerber.zip} \
Manufacturing-ready fabrication files used for PCB production. These files can be directly submitted to PCB fabrication services.

\textbf{sbcBOM.csv} \
Bill of materials listing all components required to assemble the hardware platform, including manufacturer part numbers and quantities.

\textbf{sbcPNP.csv} \
Pick-and-place file used for automated assembly of the PCB. This file enables low-cost assembly through commercial PCB assembly services.

\textbf{SimpleSBC_EnclosureTop.stl, SimpleSBC_EnclosureBottom.stl} \
3D-printable enclosure files providing mechanical protection for the assembled board while maintaining access to connectors and interfaces.

\textbf{f1c200s_simple_sbc.dts, f1c200s_simple_sbc.dtsi} \
Linux device tree descriptions defining the hardware configuration of the board, including peripheral mappings and display interfaces.

\textbf{f1c200s_simple_sbc_defconfig} \
Buildroot configuration used to generate a reproducible embedded Linux image for the platform.

\textbf{pico-uart-bridge} \
Firmware source code for the RP2040-based USB-to-UART bridge used during software development and debugging of the board.

\textbf{0001-st7789v-support-dc-gpio-8bit-spi.patch} \
Linux kernel patch providing support for the integrated ST7789V display interface used by the hardware platform.
