\section{Hardware in context}

Single-board computers (SBCs) have become an important platform for research, education, 
and rapid prototyping. 
Platforms such as the Raspberry Pi provide a low-cost and accessible method for deploying Linux-based 
applications, acquiring data, and interfacing with external hardware. 
As a result, Raspberry Pi systems are frequently adopted in laboratory environments, 
educational settings, and early-stage research prototypes.

Despite their popularity, commercial SBCs are not ideal for every application. 
Research projects often require only a subset of the functionality provided by a general-purpose 
computer, while simultaneously requiring specialized interfaces, custom form factors, 
reduced power consumption, or lower deployment costs. 
Integrating these requirements around an off-the-shelf SBC frequently necessitates the design of 
additional carrier boards, interface adapters, or custom expansion hardware, 
increasing both system complexity and overall cost.

The Simple SBC presented in this work provides an alternative design path for 
applications that require a Linux-capable embedded platform but do not require 
the full performance or ecosystem of a Raspberry Pi. 
Rather than serving as a direct replacement, 
the design demonstrates how a low-cost Linux computer can be integrated into a 
custom hardware platform using components that are readily available through 
commercial PCB fabrication and assembly services. 
The board includes the processing, memory, power regulation, storage, 
and expansion interfaces necessary to operate a Linux-based system while 
maintaining a compact and customizable architecture.

The design was inspired by prior demonstrations of minimal Linux-capable hardware, 
including the Linux Business Card project by \citeauthor{hilliard_business_card_linux_2019} 
\cite{hilliard_business_card_linux_2019} and the embedded Linux design guidance presented 
by Carlson \cite{carlson_embedded_linux}. These projects demonstrated that practical 
Linux systems can be constructed using a relatively small number of components and 
provided valuable insight into hardware design, boot processes, and software integration. 
Building upon these concepts, the Simple SBC extends the idea into a reusable research 
platform intended for customization, experimentation, and integration into larger embedded systems.

The resulting platform occupies a middle ground between highly integrated commercial SBCs 
and fully custom embedded Linux designs. It provides researchers, educators, and developers 
with an open-source reference design that can be fabricated, modified, and integrated 
into application-specific hardware while retaining the flexibility and software 
ecosystem of a Linux-based system.
