\section{Hardware description}
% Describe the hardware, highlighting the customization rather than the steps of the procedure. Highlight how it differs/which advantage it offers over pre-existing methods. For example, how could this hardware: be compared to other hardware in terms of cost or ease of use, be used in the development of further designs in a particular area, and so on.

% > Add 3-5 bulleted points to broadly explain to other researchers how the hardware could be potentially useful to them, for either standard or novel laboratory tasks, inside or outside of the original user community.

\textit{Describe your hardware, highlighting the customization rather than the steps involved in the procedure. Explain how it differs from other hardware and the advantages it offers over pre-existing methods. For example, how does this hardware compare to other hardware in terms of cost or ease of use, or how can it be used to develop further designs in a particular area? 
\vskip 0.3cm \noindent
Add 3-5 bullet points which broadly explain to other researchers - inside or outside of the original user community - how the hardware could help them, with either standard or novel laboratory tasks.}

\section*{\textit{Design files}}
% The  complete  design  files  must  be  either  uploaded  to  an  approved  online  repository,  uploaded  at the  time  of  submission  on  the  online  Editorial  Manager  submission  interface  as  supplementary materials [CAD files, videos,. . . ], or included in the body of the manuscript [e.g.  figures].  The three approved  online  repositories  are  Mendeley  Data,  the  Open  Science  Framework,  and  Zenodo. See repository instructions: https://doi.org/10.5281/zenodo.3346799

% Design files should be in preferred format for making modifications. See OSHWA’s open-source definition for details: https://www.oshwa.org/definition/

\textit{Your design files should be editable - see \href{https://www.oshwa.org/definition/}{OSHWA’s open source definition of ‘Documentation’} for further details. You must then either:}
\begin{itemize}
\item[$\bullet$]{\it Upload your design files to one of the three approved online repositories - \href{https://data.mendeley.com/}{Mendeley Data} (\href{https://doi.org/10.5281/zenodo.3346799}{instructions}), the \href{https://osf.io/}{Open Science Framework} (\href{https://osf.io/wgk7q/wiki/home/}{instructions}) or \href{https://zenodo.org/}{Zenodo} (\href{https://doi.org/10.5281/zenodo.3346799}{instructions}). We recommend this option as the repositories support versioning of files.}
\item[$\bullet$]{\it Upload your design files as supplementary materials (e.g., CAD files, videos…) to Hardware X’s online editorial system when you submit your manuscript.}
\item[$\bullet$]{\it Include your design files in the body of the manuscript (e.g., as figures).}
\end{itemize}

%
%\textit{The complete design files must be either uploaded to an approved online repository, uploaded at the time of submission on the online \href{https://editorialmanager.com/ohx/}{Editorial Manager} submission interface as supplementary materials [CAD files, videos,\dots], or included in the body of the manuscript [e.g. figures]. The three approved online repositories are \href{https://data.mendeley.com/}{Mendeley Data}, the \href{http://osf.io}{Open Science Framework}, and \href{https://zenodo.org/}{Zenodo}. See repository instructions \href{https://doi.org/10.5281/zenodo.3346799}{here}. Design files should be in preferred format for making modifications. See \href{https://www.oshwa.org/definition/}{OSHWA’s open-source definition} for details.}
%\begin{itemize}
\vskip 0.1 cm
\noindent
\textit{\underline{CAD files:} You are encouraged to use free and open source software packages for creating the files. For CAD files, \href{http://www.openscad.org/}{OpenSCAD}, \href{http://www.freecadweb.org/}{FreeCAD}, or \href{https://www.blender.org/}{Blender} are encouraged, but, if these are not available, we accept source files from proprietary CAD packages, such as Autocad or Solidworks, and other drawing packages.} 
\vskip 0.1 cm
\noindent
\textit{\underline{3D printing:} Supplementary files that facilitate digital replication of the devices are encouraged;  for example, STL files for 3D printing components. We recommend uploading CAD files to the \href{http://3dprint.nih.gov/}{\underline{NIH 3D Print Exchange}} as Custom Labware and then entering the link here.} 
\vskip 0.1 cm
\noindent
\textit{\underline{Electronics:} PCB layouts and other electronics design files can be uploaded to the \href{http://www.ohwr.org/}{\underline{Open Hardware Repository}} or other repositories or as supplementary materials.} 
\vskip 0.1 cm
\noindent
\textit{\underline{Software and firmware:} All software files used in the design and operation of the hardware should be included in the repository. Provide a description of the software and firmware and use extensive comments in the code.}
